\documentclass[11pt]{res}
\usepackage[hypertexnames=false]{hyperref}
\hypersetup{%
    pdfborder = {0 0 0},
    colorlinks,
    citecolor=blue,
    filecolor=green,
    linkcolor=blue,
    urlcolor=blue
}
\usepackage{fancyhdr}

\topmargin 0.2in \headheight 0in \headsep 0in \setlength{\textheight}{8.6in}    % page height
\oddsidemargin 0.2in \evensidemargin 0.2in \setlength{\resumewidth}{6.1in}      % page width
\newsectionwidth{0.5in}     % Indentation after section titles

\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\pagestyle{fancy}
\renewcommand{\thepage}{}   % Takes away page number
\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=.9in,bmargin=0.75in}

\newenvironment{changemargin}{\setlength{\leftmargin}{0.4in}}{\vspace{1.5mm}}

%\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

%\chead{\small James Lake}
%\rfoot{\small Updated: \today}

\begin{document}
\thispagestyle{empty}
\name{\bf{\large JAMES LAKE}\\[12pt]} % the \\[12pt] adds a blank line after name
\address{
Southern Methodist University\\
Department of Economics\\
3300 Dyer Street\\
Suite 301, Umphrey Lee Center\\
Dallas, TX 75275-0496\\
Ph: (214) 768-3274\\
}
\address{
Citizenship: Australia, USA \\
Date of Birth: February 21, 1982 \\
Website: \href{http://people.smu.edu/jlake}{http://people.smu.edu/jlake}\\
Email: \href{mailto:jlake@smu.edu}{\texttt{jlake@smu.edu}}\\
Twitter: \href{https://twitter.com/jameswesleylake}{\texttt{@jameswesleylake}}
}

\begin{resume}
\hspace{-0.5in}\makebox[6.1in]{\hrulefill}

%_______________________________________________________________________________________________________________________________________
\section{PUBLICATIONS}\vspace{5.5mm}
\begin{enumerate}
\item Contesting an International Trade Agreement, with Matt Cole (California Polytechnic State University) and Ben Zissimos (U of Exeter). \emph{Journal of International Economics}, 2021, January, 103410.
\item{Phase out tariffs, phase in trade?}, with Tibor Besedes (Georgia Tech) and Tristan Kohl (U of Groningen). \emph{Journal of International Economics}, 2020, November, 103385.
\item{Tariff bindings and the dynamic formation of Preferential Trade Agreements}, with Moise Nken (Ryerson) and Halis M. Yildiz (Ryerson). \emph{Journal of International Economics}, 2020, January, 103279.
\item{Preferential Trade Agreements: Recent theoretical and empirical developments}, with Pravin Krishna (Johns Hopkins). \emph{Oxford Research Encyclopedia of Economics and Finance}, 2019.
\item{Dynamic formation of Preferential Trade Agreements: The role of flexibility}. \emph{Canadian Journal of Economics}, 2019, 52(1), 132-177. \vspace{1.5mm}\\
{Are global trade negotiations behind a fragmented world of ``gated globalization"?}, with Santanu Roy (Southern Methodist University). \emph{Journal of International Economics}, 2017, 108, 117-136.
\item{ Free Trade Agreements as dynamic farsighted networks}, \emph{Economic Inquiry}, 2017, 55(1), 31-50.
\item{On the different geographic characteristics of Free Trade Agreements and Customs Unions}, with Halis M. Yildiz (Ryerson). \emph{Journal of International Economics}, 2016, 103, 213-233.
\item{Could tariffs be pro-cyclical?}, with Maia Linask (U of Richmond). \emph{Journal of International Economics}, 2016, 103, 124-146.
\item{Domestic political competition and pro-cyclical import protection}, with Maia Linask (U of Richmond), \emph{Review of International Economics} 2016, 24(3), 564-591.
\item{An empirical analysis of trade related redistribution and the political viability of free trade}, with Dann Millimet (Southern Methodist University), \emph{Journal of International Economics}, 2016, 99, 156-178.
\item{Costly distribution and the non-equivalence of tariffs and quotas}, with Maia Linask (U of Richmond), \emph{Public Choice}, 2015, 165(3), 211-238.
\item{Revisiting the link between PAC contributions and lobbying expenditures, \emph{European Journal of Political Economy}} 2015, 37, 86--101.
\end{enumerate}

\end{resume}
\end{document}



